Contribution Title\thanks{Supported by organization x.}

### 2021-02-02 papers/actus2021/article.tex
more formulas

\begin{equation}
formula(st)=\begin{cases}
formula' & var1(st)<var2(st)\\
0
\end{cases}
\end{equation}

@@

Applicability: ContractTerms \textbar -\textgreater{} Bool

@@

Applicability: ContractType x ContractTerm \textbar -\textgreater{}
ApplicabilityType Where applicability is either: none, always, nullable,
multiple -{}-TODO describe

In order to build superposed contract terms type for such function,
we have to resolve conflicting applicability for contract terms merged
by following the resolution rules below:

weaken(none, always) = weaken(always, none) = nullable weaken(a1,
a2) = if (priority(a1) \textgreater{} priority(a2)) a1 else a2 Where
priority(always) = 0 priority(none) = 1 priority(nullable) = 2 priority(multiple)
= 3 a1 - is applicability of a given term of first contract type to
be merged a2 - is applicability of a given term of second contract
type to be merged

@@

Generated contract is essentially a continuation chain of Marlowe
Contracts:

chainlink(eventtype, date) = receive\_data(oracle\_data(date)) -\textgreater{}
calculate\_payoff(eventtype, date) -\textgreater{} process\_payoff(date)

where receive\_data - is asking an Oracle for Marlowe Choice if needed
calculate\_payoff - calculates payoff formula. For fixed-rate contracts
this is optimised into a precalculated constant. process\_payoff -
await Deposit of payoff amount from a party: if deposit is transferred
it redirects the funds to a counterparty - otherwise it transfers
the collateral to a counterparty and closes the contract.

The chain is generated from the fixed (known in advance) schedule
of events:

contract(schedule) = receive\_collaterals -\textgreater{} initialise
state -\textgreater{} fold schedule chainlink

@@

If (condition) then perform\_something1(); continue(); else perform\_something2;
continue()

>>>>

\begin{equation}
formula(st)=\begin{cases}
formula' & var1(st)<var2(st)\\
0 & otherwise
\end{cases}
\end{equation}

@@

\noindent 
\begin{equation}
Applicability:ContractTerms\mapsto Bool
\end{equation}

@@

\noindent 
\begin{equation}
Applicability:ContractType\times ContractTerm\mapsto ApplicabilityType
\end{equation}

Where applicability could be: none, always, nullable, multiple

In order to build superposed contract terms type for such function,
we have to resolve conflicting applicability for contract terms merged
using the following resolution rules:

\noindent 
\begin{equation}
weaken(a_{1},a_{2})=\begin{cases}
nullable & a_{1}=none\wedge a_{2}=always\\
nullable & a_{1}=always\wedge a_{2}=none\\
a_{1} & priority(a_{1})>priority(a_{2})\\
a_{2} & otherwise
\end{cases}
\end{equation}

\noindent 
\begin{equation}
priority(x)=\begin{cases}
0 & x=always\\
1 & x=none\\
2 & x=nullable\\
3 & x=multiple
\end{cases}
\end{equation}

Where $a_{1}$ - is applicability of a given term of first contract
type to be merged $a_{2}$ - is applicability of a given term of second
contract type to be merged

@@

Generated contract is essentially a continuation chain of repetition
Marlowe Contracts:

\noindent 
\begin{equation}
chainlink(t)=receiveData(t)\circ calculatePayoff(t)\circ processPayoff(t)
\end{equation}

\noindent 
\begin{equation}
contract(ct)=receiveCollaterals(ct)\circ INIT(ct)\circ\prod_{t\in SCHED(ct)}chainlink(t)
\end{equation}

where $receiveData$ - is asking an Oracle for Marlowe Choice if needed,
$calculatePayoff$ - calculates payoff formula. For fixed-rate contracts
this is optimised into a precalculated constant. process\_payoff -
await Deposit of payoff amount from a party: if deposit is transferred
it redirects the funds to a counterparty - otherwise it transfers
the collateral to a counterparty and closes the contract. The chain
is generated from the fixed (known in advance) schedule of events
using $SCHED()$function from ACTUS.

@@

\begin{lstlisting}
If (condition) 
	then 
		perform_something1()
		continue() 
	else 
		perform_something2 
		continue()
\end{lstlisting}
